The Early Eocene Climate Optimum reconstructed with Bayesian multi-proxy integration

### 2022-09-03 manuscript/manuscript.Rmd
methods update

We take a hierarchical approach and infer $\mu_j$ from $m$ individual temperature observations $t_{i = 1,...m}$ at location $j$ as

@@

This structure implies that $\mu_j$ is not fixed at the mean of the temperatures $t_{i=1,...,m,~j}$ of location $j$, but is drawn (`regularised`) towards the overall logistic regression curve. The pull towards the regression curve tends to be high when $m$ is low, when the observations $t_{i=1,...,m,~j}$ are scattered, and/or when the overall standard deviation $\sigma$ is low. In practice, this has the desirable consequence that locations with few observations and large temperature differences between observations have less influence on the overall regression than well-sampled locations with consistent temperature observations.

>>>>

We infer $\mu_j$ from $m$ individual temperature observations $t_{i = 1,...m}$, derived from geochemical data, at location $j$ as

@@

Similarly, $\mu_j$ is inferred for locations with ecological proxies from the associated normal temperature distributions with a given mean and standard deviation, $mean_j$ and $sd_j$, as

$$mean_j  \sim N(\, \mu_j,sd_j).  $$

This structure implies that $\mu_j$ is not fixed at the mean proxy temperature at location $j$, <!--of the temperatures $t_{i=1,...,m,~j}$ of location $j$-->, but is drawn (`regularised`) towards the overall logistic regression curve. The pull towards the regression curve tends to be high when $m$ is low, when the observations $t_{i=1,...,m,~j}$ are scattered, and/or when the overall standard deviation $\sigma$ is low. In practice, this has the desirable consequence that locations with few observations and large temperature differences between observations have less influence on the overall regression than well-sampled locations with consistent temperature observations.
